\begin{thebibliography}{99}

\bibitem{pcmag-no-coding}
MARVIN, Rob. Building an App With No Coding: Myth or Reality.
\textit{Pcmag}[online].
 Ziff Davis, LLC. PCMag Digital Group, 2016 [cit. 2017-03-11]. Dostupné z: \url{http://www.pcmag.com/article/345661/building-an-app-with-no-coding-myth-or-reality}
\bibitem{low-code-customer-want}
RUBENS, Paul. Use Low-Code Platforms to Develop the Apps Customers Want.
\textit{CIO} [online].
IDG Communications, 2014 [cit. 2017-03-11]. Dostupné z: \url{http://www.cio.com/article/2845378/development-tools/use-low-code-platforms-to-develop-the-apps-customers-want.html}
\bibitem{low-code-accelerate}
MARVIN, Rob. How low-code development seeks to accelerate software delivery.
\textit{SD Times} [online].
BZ Media LLC., 2014 [cit. 2017-03-11]. Dostupné z: \url{http://sdtimes.com/low-code-development-seeks-accelerate-software-delivery/}
\bibitem{zoho-review}
Zoho Creator REVIEW.
\textit{Finances Online} [online].
[cit. 2017-03-11]. Dostupné z: \url{https://reviews.financesonline.com/p/zoho-creator/}
\bibitem{what-is-low-code}
CIOT, Thierry. What is a Low-Code Platform?
\textit{Progress} [online].
2016 [cit. 2017-03-11]. Dostupné z: \url{https://www.progress.com/blogs/what-is-a-low-code-platform}
\bibitem{openshift-overview}
OpenShift Origin Overview.
\textit{OpenShift Origin} [online].
[cit. 2017-03-11]. Dostupné z: \url{https://docs.openshift.org/latest/architecture/index.html}
\bibitem{cloud-computing-dummies}
HURWITZ, Judith.
\textit{Cloud computing for dummies}.
Hoboken, NJ: Wiley Pub., c2010. ISBN 978-0470484708.
\bibitem{cloud-computing}
ROME, C. H.
\textit{The cloud computing Book: The ultimate guide to mastering cloud computing}.
Fifth edition. Bernemouth: Imagine Publishing, 2015.
\bibitem{essentials-cloud}
CHANDRASEKARAN, K.
\textit{Essentials of Cloud Computing}.
Maiami: CRC Press, 2014. ISBN 978-1482205435.
\bibitem{co-je-paas}
Co je PaaS?: Platforma jako služba.
\textit{Microsoft Azure} [online].
[cit. 2017-03-12]. Dostupné z: \url{https://azure.microsoft.com/cs-cz/overview/what-is-paas/}
\bibitem{data-science-business}
FOSTER PROVOST \& TOM FAWCETT.
\textit{Data science for business what you need to know about data mining and data-analytic thinking}.
Sebastopol, CA: O'Reilly Media, 2013. ISBN 9781449374280.
\bibitem{predictive-analytics}
SIEGEL, Eric.
\textit{Predictive analytics: the power to predict who will click, buy, lie, or die}.
Revised and Updated Edition. ISBN 9781119145684.
\bibitem{big-data-anayitics}
PRASAD, Y. Lakshmi.
\textit{Big data analytics made easy}.
1. McNichols Road, Chetpet Chennai: Notion Press, 2016. ISBN 978-1-946390-72-1.
\bibitem{big-data-action}
MARZ, Nathan a James WARREN.
\textit{Big data: principles and best practices of scalable real-time data systems}.
ISBN 978-1617290343.
\bibitem{big-data-dummies}
NUGENT, Alan, Fern HALPER a JUDITH HURWITZ AND MARCIA KAUFMAN.
\textit{Big data for dummies}.
Hoboken, N.J: John Wiley, 2013. ISBN 9781118644171.
\bibitem{data-mining-principles}
BRAMER, Max.
\textit{Principles of data mining}.
3rd edition. 2016. ISBN 978-1-4471-7306-9.
\bibitem{data-mining}
HAN, Jiawei, Micheline KAMBER a Jian PEI
\textit{Data mining: concepts and techniques}.
3rd ed. Haryana, India ; Burlington, MA: Elsevier, 2012. ISBN 9789380931913.
\bibitem{minigbook}
W. CHU, Wesley, LIN, T. Y., ed.
\textit{Foundations and Advances in Data Mining}.
Springer-Verlag. ISBN 9783540808190
\bibitem{nosql}
SADALAGE, Pramod J. a Martin FOWLER
\textit{NoSQL distilled: a brief guide to the emerging world of polyglot persistence}.
Upper Saddle River, NJ: Addison-Wesley, c2013. ISBN 978-0321826626.
\bibitem{data-mining-practical}
WITTEN, I. H., Eibe. FRANK a Mark A. HALL.
\textit{Data mining: practical machine learning tools and techniques}.
3rd ed. Burlington, MA: Morgan Kaufmann, c2011. Morgan Kaufmann series in data management systems. ISBN 978-0-12-374856-0.
\bibitem{advanced-data-vizualization-platforms}
EVELSON, Boris a Noel YUHANNA.
\textit{The Forrester WaveTM: Advanced Data Visualization (ADV) Platforms}.
Corn park Drive, Cambridge, 2017. Forrester Research, Inc.
\bibitem{serverless-singlepage-apps}
RADY, Ben.
\textit{Serverless Single Page Apps: Fast, Scalable, and Available}.
1. United States of America: Pragmatic Bookshelf, 2016. ISBN 978-1-68050-149-0.
\bibitem{SPA}
MIKOWSKI, Michael S. a Josh C. POWELL.
\textit{Single page web applications: JavaScript end-to-end}.
1. United States of America: Manning Publications, 2013. ISBN 9781617290756.
\bibitem{browser-usage}
\textit{Desktop Browser Version}
[online]. [cit. 2017-05-23]. Dostupné z: \url{http://gs.statcounter.com/browser-version-partially-combined-market-share/desktop/worldwide/\#monthly-201612-201703-bar}
\bibitem{interactive-data-reily}
MURRAY, Scott.
\textit{nteractive data visualization for the web}.
Sebastopol, CA: O'Reilly Media, 2013. ISBN 978-1-449-33973-9.
\bibitem{the-ux-book}
HARTSON, H. Rex. a Pardha S. PYLA.
\textit{The UX Book: process and guidelines for ensuring a quality user experience}.
Boston: Elsevier, c2012. ISBN 978-0123852410.
\bibitem{rest-cookbook}
ALLAMARAJU, Subrahmanyam.
\textit{RESTful Web services cookbook}.
Sebastopol,CA.: O'Reilly, c2010. ISBN 978-0596801687.
\bibitem{cloud-security}
OOMMEN JOSEPH, Allen, Jaspher W. KATHRINE a Rohit VIJAYAN.
Cloud Security Mechanisms for Data Protection: A~Survey. In: \textit{International Journal of Multimedia and Ubiquitous Engineering}.
Karunya University Coimbatore, India: School of Computer Science and Technology, 2014, s. 81-90. ISSN 1975-0080.
\bibitem{scotch-jwt}
SEVILLEJA, Chris.
Scotch: Developers bringing fire to the people. \textit{The Anatomy of a JSON Web Token}.
[online]. [cit. 2017-05-03]. Dostupné z: https://scotch.io/tutorials/the-anatomy-of-a-json-web-token
\bibitem{rfc-jwt}
RFC 7519: JSON Web Token (JWT)
\textit{IETF Tools}.
[online]. [cit. 2017-05-11]. Dostupné z: \url{https://tools.ietf.org/html/rfc7519}
\bibitem{es6}
ES5, ES6, ES2016, ES.Next: What's going on with JavaScript versioning?
\textit{Benmccormick.org}.
[online]. [cit. 2017-05-11]. Dostupné z: \url{https://benmccormick.org/2015/09/14/es5-es6-es2016-es-next-whats-going-on-with-javascript-versioning/}
\bibitem{es6-coverage}
\textit{ECMAScript6 Compatibility table}.
[online]. [cit. 2017-05-11]. Dostupné z: \url{http://kangax.github.io/compat-table/es6/}
\bibitem{framework}
\textit{Top JavaScript Frameworks \& Topics to Learn in 2017}.
[online]. 2016 [cit. 2017-05-11].  Dostupné z:  \url{https://medium.com/javascript-scene/top-javascript-frameworks-topics-to-learn-in-2017-700a397b711#.fng4s5tee}
\bibitem{framework-vs-library}
Framework vs Library: which one is better?
\textit{Void Canvas}.
[online]. 2017 [cit. 2017-05-11]. Dostupné z: \url{http://voidcanvas.com/framework-vs-library-one-better/}
\bibitem{material}
\textit{Material design: Introduction}.
[online]. [cit. 2017-05-11]. Dostupné z: \url{https://material.io/guidelines/#introduction-goals}
\bibitem{bootstrap}
\textit{What is Bootstrap and How Do I~Use It?}.
[online]. [cit. 2017-05-11]. Dostupné z: \url{https://www.taniarascia.com/what-is-bootstrap-and-how-do-i-use-it/}
\bibitem{patternfly}
\textit{Patternfly: Frequently Asked Questions}.
[online]. [cit. 2017-05-11]. Dostupné z: \url{https://www.patternfly.org/get-started/frequently-asked-questions/}
\bibitem{oidc}
\textit{OpenID: Welcome to OpenID Connect}.
[online]. [cit. 2017-05-11]. Dostupné z: \url{http://openid.net/connect/}
\bibitem{saml}
\textit{The Basics of SAML}.
[online]. [cit. 2017-05-11]. Dostupné z: \url{http://www.gigya.com/blog/the-basics-of-saml/}
\bibitem{keycloak}
\textit{Keycloak: about }.
[online]. [cit. 2017-05-11]. Dostupné z: \url{http://www.keycloak.org/about.html}
\bibitem{ibm-ster}
\textit{IBM: About Sterling External Authentication Server}.
[online]. [cit. 2017-05-11]. Dostupné z: \url{https://www.ibm.com/support/knowledgecenter/en/SS4T7T_2.4.1/com.ibm.help.seasimplementationguide.doc/SEAS_About_SEAS.html}
\bibitem{ADFS}
\textit{Active Directory Federation Services}.
[online]. [cit. 2017-05-11]. Dostupné z: \url{https://msdn.microsoft.com/en-us/library/bb897402.aspx}
\bibitem{powerbi}
\textit{What is Power BI? }.
[online]. [cit. 2017-05-11]. Dostupné z:  \url{https://powerbi.microsoft.com/en-us/what-is-power-bi/}
\bibitem{watson}
\textit{BM Watson Analytics: Analytics made easy }.
[online]. [cit. 2017-05-11]. Dostupné z: \url{https://www.ibm.com/analytics/watson-analytics/us-en/}
\bibitem{microstrategy}
\textit{What is MicroStrategy? }.
[online]. [cit. 2017-05-11]. Dostupné z: \url{http://searchbusinessanalytics.techtarget.com/definition/MicroStrategy}
\bibitem{sap}
\textit{Business Objects or HANA? A~guide to SAP analytics environments}.
[online]. [cit. 2017-05-11]. Dostupné z: \url{http://searchsap.techtarget.com/essentialguide/Business-Objects-or-HANA-A-guide-to-SAP-analytics-environments}
\bibitem{crm}
\textit{What is customer relationship management (CRM)}.
[online]. [cit. 2017-05-11]. Dostupné z: \url{http://searchcrm.techtarget.com/definition/CRM}
\bibitem{kiss-ab}
\textit{Kissmetrics Academy: LEARN HOW KISSMETRICS CAN OPTIMIZE YOUR MARKETING}.
[online]. [cit. 2017-05-11]. Dostupné z: \url{https://blog.kissmetrics.com/google-analytics-and-kissmetrics/}
\label{LastPage}
\end{thebibliography}
